\documentclass[10pt,a4paper]{moderncv}
\setlength{\parskip}{0pt}
% moderncv themes
\moderncvtheme[blue]{classic}                  % optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)


% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths



% personal data
\firstname{Angus}
\familyname{Scott}
\phone{+447920104841}                      % optional, remove the line if not wanted
\email{angusscott@me.com}                      % optional, remove the line if not wanted

\homepage{uk.linkedin.com/in/angusiscott}              % optional, remove the line if not wanted
%\extrainfo{bitbucket.org/superkom}				% optional, remove the line if not wanted




%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\vspace*{-2\baselineskip}
\section{Education}

\cventry{2010 - 2015}{BSc Artificial Intelligence and Computer Science}{2:1}{University of Edinburgh}{{Edinburgh}}{} 




\section{Experience}

\cventry{June 2015 - Current}{Application Developer, Technology Intern}{J.P.Morgan Chase \& Co}{}{{London}}{As part of my second internship with J.P.Morgan I am working as an Application Developer with the Fixed Income Technology team, within Asset Management. I am developing a web application using Bootstrap, JavaScript and JQuery for the client, along with Java and SQL for the server. The application allows for changes to be made to production databases by application support, without the need to write SQL queries directly. I have also been exposed to the portfolio management and trade execution systems developed by my team, and to business users across Asset Management.}

\cventry{June 2014 - Sept 2014}{Business Analyst, Technology Intern}{J.P.Morgan Chase \& Co}{}{{London}}{I worked as a Business Analyst in the Project Management team within Global Technology Infrastructure (GTI). During my internship I worked on three main projects: Firstly, creation of a project repository using SharePoint; secondly, automating the creation of reports using VBA, and thirdly, I worked on part of the exit strategy from an important UK based data centre. I also gained exposure to other parts of the business through shadowing, in particular, the Market Data and Trading Technologies teams. }

\cventry{June 2013 - Dec 2013}{Invention Database Intern}{Edinburgh Research and Innovation}{University of Edinburgh}{{Edinburgh}}{I setup and customised the Inventor Portal web module for Inteum C/S. This enables inventors to submit invention disclosures digitally to the University for patenting/licensing. I was involved in the entire project lifecycle. This entailed defining the project with the help of inventors and business developers, setting up the portal in consultation with IT staff, customising it with the aid of the brand manager and finally creating documentation for all users. During my internship I was also provided with opportunities to increase my insight in technology transfer and IP management. I have continued this role as a consultant.}

\cventry{June 2011 - Current}{Student Ambassador}{University of Edinburgh}{}{{Edinburgh}}{I work as a Student Ambassador for the School of Informatics. This involves presenting to groups of up to 100 students and so my effective communication skills are key. At the University open days I am involved in introducing students to University life and providing information about Informatics courses and the School. Post-application open days cover similar subjects but in significantly more detail, with prospective students being much better informed making the Q\&A sessions both challenging and interesting.  I have received very positive unsolicited feedback from both students and parents about my involvement.}


\cventry{Jan 2010 - Jan 2011}{Commis Chef}{Cromlix House Hotel}{}{{Dunblane}}{Previously, I worked as a Commis Chef. The quality of food offered by Cromlix House was high and so the work involved balancing  quality and time available to ensure that tasty but complex and attractive food was served hot and on time. I was part of a very hard working team working in a high pressure environment and the only way we could ensure things were going to be on time whilst retaining excellent quality standards was if we worked together effectively. Upon leaving, I was offered a salary increase and the opportunity to fast track my career path, by both my boss and the owner of the restaurant to entice me to stay.}
\enlargethispage{3\baselineskip}
\section{Computer Skills}
\cvline{Competent}{Python, Java, MATLAB, HTML/CSS/Bootstrap, SQL}
\cvline{Novice}{Prolog, Haskell, Javascript, Visual Basic}
\cvline{Tools/Skills}{Machine Learning, Data Science, Natural Language Processing, Information Retrieval, Git, Hadoop, XML, JSON, \LaTeX, JUnit}
\section{Example Projects}
\cvline{Political Classification}{As part of my Undergraduate final year project, I am built a collection of classifiers to classify a users political persusasion using data compiled from Twitter. The training and test data was composed from tweets compiled during the Scottish Referendum on Independence, and the classification task involves classifying whether a user was more likely to vote either Yes, No or Unknown based on a number of features obtained from tweets. }
\cvline{System Design Project}{With the help of my team, we built a pair of football playing robots. These robots viewed the pitch using a camera feed, and would then detect the ball, opponents, etc, which was in turn fed into a strategy system. The strategy system would then select appropriate strategies and send movement commands to the robots.}

\cvline{Cryptopear}{A product of a recent appathon hosted by the University of Edinburgh on behalf of SVC2UK, a project written in Python that allows for authenticated anonymous chat. We won the competition and our prize included reception in Downing Street. and photo opportunity with George Osborne }

\cvline{Mining With A Cup}{Aggregated tweets using the Twitter API, and mined those for information relating to the 2014 Football World Cup as a joint project with a friend. We found a significant correlation between number of mentions of a team, and the odds given by bookmakers. We also saw strong correlation between the scores predicted by users and the bookmakers odds during the group stages.}

\section{Societies}

\cventry{May 2012 - May 2013}{Treasurer}{University of Edinburgh Gaming Society (GameSoc)}{University of Edinburgh}{{Edinburgh}}{My role was to maintain the accounts for the society and to help out with events such as LANs and pub nights. I was also one of the main points of contact between CompSoc and GameSoc.}

\cventry{May 2011 - May 2012}{President}{University of Edinburgh Computing Society (CompSoc)}{University of Edinburgh}{{Edinburgh}}{Formerly I was the President of the University of Edinburgh Computing Society (“CompSoc”), which runs events and offers support to our 300+ members. We are one of the largest University computing societies in the UK and one of the most highly regarded. Whilst I was President we had a five fold increase in sponsorship funds, which I helped obtain by pitching to various companies. We also increased the number of events and improved the content of the others. I was the driving force behind this. The STMU, which is our flagship event, is a chance for guest speakers to come and talk tech with our members. At our first meet-up we had over 100 attendees, beating all previous records, with talks from some of the largest and most innovative companies in industry including Amazon, Citibank, Deloitte and Bloomberg.}



\section{Sports \& Interests}

\cvline{}{I am a member of the squash club at the University and frequently play squash with friends. I also completed Tough Mudder this year. This, was a major achievment for me. I began training in January, having never raced before, but managed to successfully complete the exhausting 12 mile course.}

\cvline{}{During my year as a Commis Chef I also attended classes at Nick Nairn Cookery School and at the Edinburgh New Town Cookery School, my enthusiasm for cookery has continued since, and I continue to attend recreational cookery classes when I can.}
\enlargethispage{3\baselineskip}
\section{Skills}
		\cvline{}{I align my strengths into three distinct areas: }
		\cvline {Problem Solving} {During my time at ERI I was asked to provide an accurate solution based on a project specification, I successfully implemented this and worked through problems that arose. This reflects the skill set required for my degree.}
		\cvline{Versatility}{ In previous roles I have worked efficiently in a wide range of environments, including both team and independent based workplaces such as Cromlix House and my treasurer role. }
		\cvline{Effective Communication} {As President for Compsoc and as a Student Ambassador I have developed strong communication and interpersonal skills. }


\end{document}